Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-05 ltx/data_paper/DataPaper.tex
added comment on discussion
added a comment on condition under which Xi4 is invertible

variable $\boldsymbol\Xi_4$ is symmetric and positive-definite by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields

@@

The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get

@@

\begin{itemize}
	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate.  
\end{itemize}

>>>>

noting that variable $\boldsymbol\Xi_4$ is symmetric by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields

@@

We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on. The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get

@@

\begin{itemize}
	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property (I guess) using EM with URTSS
\end{itemize}
